---
title: "Week 3 Assignment"
author: "Simone"
date: "March 6, 2020"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 5)
```

## Dataset

### Description
**mtcars** (*Motor Trend Car Road Tests*)  
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

### Type of plot
We are going to build an interactive **scatter3d** plot using the **plotly** library, with the variable **wt** (*Weight (1000 lbs)*) on the x-axis, the variable **qsec** (*1/4 mile time*) on the y-axis, and the variable **mpg** (*Miles/(US) gallon*) on the z-axis. Furthermore, the color of the markers is based on the variable **am** (*Transmission: 0 = automatic, 1 = manual*)

## Code to create the plot (1)

```{r plot_1, echo = TRUE}
## Load the libraries
library(plotly)
library(datasets)
data(mtcars)

## Transform the variable am as a factor
mtcars$am[mtcars$am == 0] <- 'Automatic'
mtcars$am[mtcars$am == 1] <- 'Manual'
mtcars$am <- as.factor(mtcars$am)
```

## Code to create the plot (2)

```{r plot_2, echo = TRUE}
## Build the plot
p <- with(mtcars, plot_ly(x = wt, y = qsec, z = mpg,
                          type = "scatter3d",
                          mode = "markers",
                          color = factor(am))) %>%
  layout(autosize = T,
         scene = list(xaxis = list(title = "Weight (1000 lbs)"),
                      yaxis = list(title = "1/4 mile time"),
                      zaxis = list(title = "Miles/(US) gallon"),
                      camera = list(eye = list(x = 1.6,
                                               y = 1.6,
                                               z = 0.5))))
```

## Slide with Plot

```{r plot_3}
p
```